CLT Results

### 2022-04-10 analysis/clt_data_processing.Rmd
add more data for run on cluster

```{r}
# MPI
# rsync -zaP ccp-odcJ:/srv/ccp-odc/clt-extended/data/ ~/Work/Local/Quantex/vocab/data/clt_raw_data/

# ZAS und kischawi

# rsync -zaP ccp-odcJ:/srv/ccp-odc/clt-zas/data/ ~/Work/Local/Quantex/vocab/data/clt_raw_data_zas/
```

@@

```{r, warning=F}
# files_zas <- str_subset(dir("../data/clt_raw_data_zas/", pattern = ".json"), pattern = "DELETE", negate = TRUE) 
# 
# files_zas <- files_zas[!files_zas %in% pilot]
# 
# raw_data_zas <- data_frame()
# for (f in files_zas) {
#   jf <- paste("../data/clt_raw_data_zas/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   subjID <- jd$meta$subjID
#   order <- jd$meta$order
#   add <- as_data_frame(jd$data) %>% mutate(subjID = subjID,
#                                                  order = order)
#   raw_data_zas <- bind_rows(raw_data_zas, add)
# }
# 
# proc_data_zas <- raw_data_zas%>%
#   mutate(subjID2 = subjID)%>%
#   separate(subjID2, into = c("bday","sex","postcode"), sep="_")%>%
#   mutate(test_day = substr(timestamp, 0,10),
#          test_day = as.Date(test_day,"%Y-%m-%d"),
#          bday  = as.Date(bday,"%d-%m-%Y"),
#          age = as.numeric(difftime(test_day, bday, units = "days"))/365.25,
#          sex = tolower(sex))
# 
# data_zas <- proc_data_zas%>%
#   left_join(aoa)%>%
#   select(-timestamp)%>%
#   ungroup()%>%
#   mutate(age_group = substr(age,0,1))%>%
#   select(-bday, -test_day)%>%
#   filter(!is.na(age))%>%
#   ungroup()

@@

data%>%
  filter(source == "mpi")%>%
  summarise(n = length(unique(subjID)))

@@

@@

```{r}
data%>%
  group_by(subjID)%>%
  summarise(age = round(mean(age),2))%>%
  ggplot(aes(x = age))+
  geom_jitter(aes(y = 0),width =0, height = 0.02, pch = 1, alpha =.75)+
  geom_density()+
  #ylim(-1,1)+
  theme_minimal()

@@

```{r}
p2 <- data%>%
  group_by(subjID, age)%>%
  tidyboot_mean(col = correct)

ggplot(p2, aes(x = age, y = mean))+
  #stat_cor()+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .25)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  labs(x = "Age", y = "Proportion correct")+
  ylim(0,1)+
  xlim(3,8.2)+
  theme_minimal()
```

>>>>

```{r}
# MPI
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/clt-extended/data/ ~/Work/Local/Quantex/vocab/data/clt_raw_data/")

# ZAS und kischawi
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/clt-zas/data/ ~/Work/Local/Quantex/vocab/data/clt_raw_data_zas/")
```

@@

```{r, warning=F}
files_zas <- str_subset(dir("../data/clt_raw_data_zas/", pattern = ".json"), pattern = "DELETE", negate = TRUE)

files_zas <- files_zas[!files_zas %in% pilot]

raw_data_zas <- data_frame()
for (f in files_zas) {
  jf <- paste("../data/clt_raw_data_zas/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  subjID <- jd$meta$subjID
  order <- jd$meta$order
  add <- as_data_frame(jd$data) %>% mutate(subjID = subjID,
                                                 order = order)
  raw_data_zas <- bind_rows(raw_data_zas, add)
}

proc_data_zas <- raw_data_zas%>%
  mutate(subjID2 = subjID)%>%
  separate(subjID2, into = c("bday","sex","postcode"), sep="_")%>%
  mutate(test_day = substr(timestamp, 0,10),
         test_day = as.Date(test_day,"%Y-%m-%d"),
         bday  = as.Date(bday,"%d-%m-%Y"),
         age = as.numeric(difftime(test_day, bday, units = "days"))/365.25,
         sex = tolower(sex))

data_zas <- proc_data_zas%>%
  left_join(aoa)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age_group = substr(age,0,1))%>%
  select(-bday, -test_day)%>%
  filter(!is.na(age))%>%
  mutate(correct = ifelse(targetWord == chosenWord, 1,0))%>%
  mutate(targetWord = ifelse(targetWord == "kangoroo", "kangaroo", targetWord))%>%
  left_join(aoa)%>%
  ungroup()

@@

@@

# Participants

```{r}
# filtered_data%>%
#   filter(trial == 1)%>%
#   select(test_day,subjID)%>%
#   distinct(subjID, .keep_all = T)%>%
#   write_xlsx("../data/participated_06_04_22.xlsx")
```

@@

```{r}
data%>%
  group_by(source,subjID)%>%
  summarise(age = round(mean(age),2))%>%
  ggplot(aes(x = age))+
  geom_jitter(aes(y = 0, col = source),width =0, height = 0.02, pch = 1, alpha =.75)+
  scale_color_colorblind()+
  geom_density()+
  #ylim(-1,1)+
  theme_minimal()

@@

```{r}
p2 <- data%>%
  group_by(source,subjID, age)%>%
  tidyboot_mean(col = correct)

ggplot(p2, aes(x = age, y = mean))+
  #stat_cor()+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, col = source), alpha = .25)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  scale_color_colorblind()+
  labs(x = "Age", y = "Proportion correct")+
  ylim(0,1)+
  xlim(3,8.2)+
  theme_minimal()
```

### 2022-04-10 analysis/clt_irt_analysis.Rmd
add more data for run on cluster

```{r}
library(mirt)

remove <- c("telephone", "strawberry" ,"plane" ,"snake" ,"fish", "belt")

firt_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(!targetWord %in% remove)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 5000), SE = T)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

anova(firt1,firt2)
anova(firt2,firt3)

@@

>>>>

```{r}
remove <- c("telephone", "strawberry" ,"plane" ,"snake" ,"fish")

firt_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(!targetWord %in% remove)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)
```

```{r}
# dimensionality

library(mirt)

@@

library(psych)

unidim(firt_dat, cor = "tetrachoric")

@@

```{r}
firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000), SE = T)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

anova(firt1,firt2)
anova(firt2,firt3)
```
